Annotation-Based Empirical Performance Tuning Using Orio

### 2009-02-12 doc/papers/ipdps09/results.tex
git-svn-id: https://svn.mcs.anl.gov/repos/performance/orio@434 e7ad4b5f-b827-0410-872f-f7f4bc3d1efb
git-svn-id: https://svn.mcs.anl.gov/repos/performance/orio@436 e7ad4b5f-b827-0410-872f-f7f4bc3d1efb

\begin{figure*}%[htb]
\begin{center} 
  \subfigure[Sequential (T=500)]{ 
  \includegraphics[width=.45\textwidth]{figures/seidel-cookie/seq.eps} 
  \label{fig:seidel-cookie-seq} } \subfigure[Parallel (T=500, 
  N=4000)]{ 
  \includegraphics[width=.45\textwidth]{figures/seidel-cookie/par.eps} 
  \label{fig:seidel-cookie-par} } 
\end{center}
\caption{3-D Gauss-Seidel performance on eight-core Intel machine.} 
\label{fig:seidel-cookie-results} 
\end{figure*}

\begin{figure*}%[htb]
\begin{center} 
  \subfigure[Sequential]{ 
  \includegraphics[width=.45\textwidth]{figures/lu-cookie/seq.eps} 
  \label{fig:lu-cookie-seq} } \subfigure[Parallel (N=4000)]{ 
  \includegraphics[width=.45\textwidth]{figures/lu-cookie/par.eps} 
  \label{fig:lu-cookie-par} } 
\end{center} 
\caption{LU Decomposition performance on eight-core Intel machine.} 
\label{fig:lu-cookie-results} 
\end{figure*}

@@

Figure~\ref{fig:fdtd-2d-cookie-par} shows the multicore performance
obtained for $tmax=500$ and $nx=ny=2000$. The results indicate that
whereas icc is unable to autoparallelize the code, Pluto detects the
existence of pipelined parallelism and then successfully parallelizes
the code. Locality-exploiting optimizations by Orio additionally
improve the Pluto performance by up to 78\%. Moreover, we observe
that because of memory contention between the two quad-core Intel
processors, the speedup of both the Pluto and Orio codes slightly
decreases when the number of cores used is greater than four.

>>>>

\begin{figure*}%[htb]
\begin{center} 
  \subfigure[Sequential (T=500)]{ 
  \includegraphics[width=.45\textwidth]{figures/seidel-cookie/seq.eps} 
  \label{fig:seidel-cookie-seq} } \subfigure[Parallel (T=500, 
  N=4000)]{ 
  \includegraphics[width=.45\textwidth]{figures/seidel-cookie/par.eps} 
  \label{fig:seidel-cookie-par} } 
\end{center}
\caption{3-D Gauss-Seidel performance on eight-core Intel Xeon.} 
\label{fig:seidel-cookie-results} 
\end{figure*}

\begin{figure*}%[htb]
\begin{center} 
  \subfigure[Sequential]{ 
  \includegraphics[width=.45\textwidth]{figures/lu-cookie/seq.eps} 
  \label{fig:lu-cookie-seq} } \subfigure[Parallel (N=4000)]{ 
  \includegraphics[width=.45\textwidth]{figures/lu-cookie/par.eps} 
  \label{fig:lu-cookie-par} } 
\end{center} 
\caption{LU decomposition performance on eight-core Intel Xeon.} 
\label{fig:lu-cookie-results} 
\end{figure*}

@@

Figure~\ref{fig:fdtd-2d-cookie-par} shows the multicore performance
obtained for $tmax=500$ and $nx=ny=2000$. The results indicate that
whereas icc is unable to auto-parallelize the code, Pluto detects the
existence of pipelined parallelism and then successfully parallelizes
the code. Locality-exploiting optimizations by Orio additionally
improve the Pluto performance by up to 78\%. Moreover, we observe
that because of memory contention between the two quad-core Intel
processors, the speedup of both the Pluto and Orio codes slightly
decreases when the number of cores used is greater than four.
